\documentclass[a5paper]{report}%{memoir}%{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{fontspec}

% always indent first line after \section{bla}
\usepackage{indentfirst}

\defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
\setmainfont{Noto Sans}%Serif}
\setmonofont{Hack}

\usepackage
[ a5paper
, top=2cm
, bottom=2cm
, left=1.75cm
, right=1.75cm
, marginparwidth=0.75cm
]{geometry}

\author{Sio Kreuzer}
\title{Escape to Uranus}


\newcommand{\coo}{CO$_2$ }

\newcommand\spacer{{\center{$\cdots\\$}}}

\begin{document}

\chapter{Prologue}

I was sitting around in Mission Control, in Hawthorne, California.
In the United States, on boring old Earth. In an office chair that at first
glance looks comfortable, but turns out to just be vaguely uncomfortable and
really, really cheap when you actually sit down on it. This vague discomfort
eventually became unbearable and encouraged mine and many of my colleague's
frequent coffee breaks.

So I was just minding my own business, really - making sure all the near-Earth
automated manufacturing space stations had their software updated, that none of
them crashed into each other, that sort of thing. Since that was seen as a
rather lowly job, I was relegated to a big open-plan side office, away from the
flashy big mission control screens, and had to share that office with about
fifty other people, give or take twenty, depending on the shift and how many
people had burned out and not been replaced yet.

So anyway, I was just about to SSH (yeah, old technology, and the primary reason
we couldn't remotely update anything past a certain point away from Earth) into
a Lunar aluminium smelting complex's central control server, typing away letter
by letter and verifying they actually arrived because our transmission protocols
were buggy like that. Then I got forcibly disconnected and my screen started
showing a livestream from somewhere.

I was just about to instinctively click it
away so as to not get yelled at, only to find out that, controls wise, I was
completely locked out of my work computer. Might as well pay attention to the
screen, then. On it was a 30-something looking woman with insanely blue, long,
and somewhat unkempt hair, almost like she'd just got out of bed ten minutes
ago; \textit{Fuck, I wish I had hair like that. Or a girlfriend with hair like
  that, I'm not that picky.} was just about the only thing to go through my head
for entire few seconds before I caught myself and started paying attention to
the stream again. Behind her was a rough-looking wall, obviously made out of a
single sheet of steel. Standard company space station construction. Or, I
suppose, planetary habitat construction, too. Gotta remind myself the stuff they
get on Mars is fucking luxurious compared to what they get everywhere else.

She was obviously trying to verify that her streaming equipment was working.
After a few seconds, she nodded at something or someone I couldn't see,
and turned to the camera. She tucked a stray hair that had fallen into her face
behind her ear, and started reciting what was clearly
a badly-rehearsed speech into the camera.

``Hello everyone! Those here in the Jovian system and around the Trojans
may already know me well, but
for everyone tuning in from Earth, Luna, Mars or the many space stations around
them: I'm Vic Vladeva and my company title with SpaceTech
is `Head of Operations for the Jovian System'. That means I am, on paper,
responsible - towards the board of the company, anyhow - for all of SpaceTech's
operations around Jupiter, as well as the space stations and asteroid mining
around it's $L_4$ and $L_5$ Lagrange points. Call me Vic, everyone does.''

\textit{Huh, neat. She seems nice. Wish I was out there, instead of here. Hell,
  even if she's completely horrible, she's gotten me a minute of free time so
  far, and probably annoyed the fuck out of my bosses.} I thought, while Vic
continued speaking.

``Oh yeah, some of you on Earth and Mars may be confused why you're seeing me on
your screens. I was told by a guy down in IT that he was bored out of his mind,
and that they decided to finally showcase what fun things could be accomplished
with the shit security on the company network. Thus the only semi-intentional
broadcast to everyone down at the mission control facilities.''

``Now that we've got that out of the way, time to get to the really important
bit of this announcement: We here in the Jovian system have had it with
SpaceTech and are going to do our own thing from now on. To this end, 95\% of
the workforce in the Jovian system have ratified our new constitution, which is
also known as the Dorsa Brevia document. We've seeded that on a fair few places
online, so anybody interested should be able to obtain a copy. To wit: we
function as a loose connection of communities, with a common set of rules and
values, and a common military. We're happy to welcome new members to this loose
federation of sorts, and will aid those who do join us. Furthermore, we
currently occupy the Jovian, Saturnian, and Uranian systems, and intend to hold
them. We intend to allow immigration, only restricted by technical ability.
Nobody who makes it as far out as the Jovian system will be turned away, but we
may tell you not to make the journey just yet. Again, the Dorsa Brevia document
details all of this, if you want to know more. It also details how to contact
us, in case you'd like to join us out here.''

I immediately took out my phone and looked up the Dorsa Brevia document. No luck
on social media. No big surprise. Various image boards?
Troll, troll, absolutely abhorrently bad troll... no hit, huh. Let's check the
bay. Oh, would you look at that... there we go. Of course, while I was doing
that, the woman speaking for the not-OPA hadn't finished her speech.

``On a somewhat personal note: Mr CEO? Fuck you. Try to get anywhere close to
here and we'll do to you as you've done to many of us.''

\textit{Oh, now I \textnormal{really} like her.}

``Now, the pitch: should any of you wish to join us, we'll try to coordinate
you. But that may be difficult. We do really need people, qualified or not, we
don't care. Organise amongst yourselves, preferably via unions. Well, whatever
unions remain in your area. Keep in mind that due to the journey times, and due
to what we're doing being sort of illegal, this is likely a one-way trip. On the
plus side, we offer the gerontological treatments to everyone, regardless of
position, status, or who they know. That's how I look 35, if you were wondering.
I'm actually 85, if memory serves? So yeah, if you do come here, while for now
it's one way, you do get to live a whole lot longer than you would down with the
megacorps. For those of you on Mars...''

She continued, but I knew that beyond that, things were largely irrelevant to
me. People that far out and that old usually had no idea what it took to get off
Earth these days, and so her advice probably wasn't going to be helpful beyond
telling everyone where to meet.

A few seconds later, the document was on my phone, and I was idly browsing it.

\textit{Looks like they're Anarchosyndicalists, huh. No big surprise there. Do
  they even need someone like me? I mean hell, what can I even do? Use the
  bloody terminal? Then again, she said they'd take anyone at all, so...}

I looked up what unions were active in my area. This turned out to be difficult,
as while union membership has risen sharply in recent years, so has regulation
pertaining to who can and who cannot join a union. So most unions don't even
bother having an internet presence. And I wasn't a member. Yet. I'd always been
meaning to get around to it.

It took some searching, and I probably missed a good portion of the stream going
on. Oh well, if there was anything important there, I could always read it up on
the 'net later again, but I found a union that might have some of their regular
get-togethers frequented by like-minded people that wanted a better life. Even
if that better life meant never being outdoors without a space suit ever again.

It was at just about this point that the discomfort caused by my chair that I
mentioned earlier started to go from ``vaguely tolerable'' to ``constantly on
the forefront of my mind please go away oh eris why isn't it going away I have
stuff to do''. Since Vic was done talking politics and had started answering
questions posed by people from the Jovian system, I decided this was a good time
to get up and get myself some coffee.

As I hefted myself out of my too-small office chair, my annoyingly brown hair
fell in front of my face. \textit{I need to remember to bring some hair ties. Or
just quit so I can dye it whatever color I want so being reminded of it's color
doesn't annoy me anymore.} I thought, while trying to shimmy out of the weird
corner spot my desk was in without bumping my hips or thighs into any tables on
the way, grabbing my mug off my desk just as I was coming around to the other
side. Not bumping into anything proved difficult, because desks appeared to
generally be built at just the right height for me to bump my hips into them. It
didn't help that at 6 feet tall and generally quite wide, I outsized most
people, so my comfort was in no significant way catered to. I suppose it's
better than airplane seats and moving around an airplane, but that's setting the
bar so low it takes digging to get there. Oh well, at least I don't bump my head
into doorframes all the time.

Just as I'd finished that thought, I'd arrived at the kitchen, wherein the
blessed coffee making machine stood. Just as I'd arrived there, I realized I
\textit{really} needed some coffee right about now. I hadn't slept very well the
past night and it was really starting to catch up to me. I was getting tired
again, and it took me an appreciable amount of time to notice my colleague
Melissa also standing in the room, leaning against one of the kitchen work
surfaces slowly sipping her coffee. She drank her coffee black, and could
somehow tolerate the cheap, shit coffee that came out of the office coffee maker
without putting an enormous amount of milk and sugar in it. I still envied that.
She always felt small to me, though she must've been about average height. She
was pretty, in a very soft and round kind of way. She was also one of the few
people here I actually liked to be around, and the feeling was mutual. We never
went beyond being friendly, though. Just not a thing I was comfortable with
going for with a work colleague, and though at times it felt like she might be
interested, she felt the same way. She was also talking to me.

``Hello, Earth to Alex. You okay?''

``Sorry. I think I'm fine? Just tired. The stress from being understaffed is
making me sleep really badly.'' I said as I put my mug under the coffee maker
and pressed a button that ought to give me what the system referred to as a
'Latte Macchiato'.

``Yeah, I get that. Did you see the livestream? Nobody can work and I've heard
loud managerese swearing from multiple meeting rooms nearby.'' she told me,
Schadenfreude clearly evident in the way she'd said the last part.

``Yup. Thinking of taking them up on the offer. The closest thing I've got to
anyone keeping me here is probably you. And I guess a few of my high school and
college friends that didn't turn out to be huge dicks. So yeah, I want to go. We
both know this place isn't the best, and it's the only real option for me. Well,
except that one new one. I'm planning on going out as soon as possible, see if I
can find out some more about that.'' I just told her what was going on in my
head, forgetting to apply my usual 'at work' filter.

``Huh. Let me know what you find out. It's obviously not quite that bad for me,
but... let's say there's significant room for improvement and I'd like to
explore that, if you get what I mean.''

``Will do.'' I reassured her, and got my now filled mug.

We spent a few more minutes just drinking coffee and idly chatting, until we
figured we ought to look busy for when the manglers finished their shouting
match and so we returned to our desks to keep watching Vic answer people's
questions and pretend to be trying to get our computers under control again.

\spacer

So two days later, I went to the bar the union's members met at every week.
Their admittedly very poorly and infrequently maintained website said they
welcomed people interested in joining, or who had questions, coming to these
weekly get-togethers. I doubt they ever anticipated this type of thing.

Upon entering the establishment, I immediately made my way to the bar. If I was
going to talk to people I didn't already know, I was sure as all hell not going
to do it sober. My social anxiety wasn't exactly great about permitting that. I
got the bartender's attention, she gestured for me to wait my turn, and after a
while I ordered a locally brewed IPA, hoping if I didn't get anything good I'd
at least get something interesting.

\spacer

Several bottles of surprisingly good local craft beer and about two hours in,
I'd almost forgotten what I was here to do again, when it dawned on me. Now
somewhat less inhibited, I took my jacket and my beer, gestured to the bartender
that I was going to sit at a table, and made my way to the union people sitting
at the back of the place, who were currently busy getting swamped with questions
and getting progressively more annoyed at having their conversation interrupted,
while doing their best not to show it.

As I got there, I surprised myself and them by getting their attention and
proclaiming: ``Hi. I'm Alex. Two things: For one, I'd like to join. Or, failing
that, get some guidance on getting the unionization process started at my
workplace. Two, I'm interested in getting off this planet and as far away as
possible from working 60 hours a week just to make rent that's continuously
being increased.''

``Name's Carl. And wouldn't we all, Mr. Alex. Just having the option... okay,
some of us really don't want to leave. But yeah, just having the option of going
somewhere things are better? It's a pretty nice concept.'' an older fellow with
a full, gray beard wearing a hawaiian shirt and cargo shorts responded to me, in
a tone indicating he'd been saying some very similar sentences to a lot of
people today.

``It's \textit{Miss Alex}, actually.'' \textit{And this is why I don't like
  talking to people.} ``I should take it you don't consider it realistically
possible, then?'' I briefly retorted.

He looked at me in an indecipherable way, went ``Well then, Miss Alex it is.'',
and proceeded to explain in the same tone from before: ``We
don't know anything about the logistics of it.  We've got some people with a
passing interest in spacecraft, the kinda people to play Kerbal Space Program,
but that's about it. And so
far, almost everyone who's asked us to help them has had no clue, either. We've
had no luck contacting the people at Jupiter with people's questions in hand.
And the remaining few who came here and know how to do this stuff? Well, they
don't have the time to assist us in any way, what with working 80 hour work
weeks with 'mandatory overtime' and all that. So... unless you have some time,
and a bit of an idea how one could even go about this, you'll have to ask
someone else.''

``You only contacted the people in the Jovian system at the start of your
meeting?'' I was quietly talking to myself again, a habit I'd developed over the
years of living alone and spending most of my time alone. ``No wonder you got no
response, Jupiter is at least 40 minutes at straight-line lightspeed away.
That's 1 hour, 20 minutes round trip. And that's ignoring that your message has
to propagate across the repeater network, to Mars, then from there to Jupiter.
You're looking at about 2 to 3 hours, round trip. And that's assuming they can
get to you immediately.''

\textit{Somebody} had evidently heard and even understood my mumbling to myself.
``Huh, yeah, good point. And it \textit{is} genuinely helpful, so stop just
mumbling to yourself.''

``I don't really know much of this stuff, though.''

``Whatever. If you know enough to have a general clue, we could really use your
help. So? You said you wanted to join? Ever thought about learning some basics
of how to organize and how to get people to more or less work together? We
honestly would like to assist in this, but we just don't know much. We've got
people's numbers, we can get people organized. Enough. We think. We really
need some help with what's feasible, what's infeasible, what we can do. That
sort of thing. We need someone to ask stupid questions, at the very least.''

``Uhhh. Thought about yes?'' I said, caught off balance by the idea that someone
\textit{wanted} me to help them.

The rest of the evening went by quickly, as I slowly got more inebriated and met
a whole bunch of people whose names and faces would no doubt only be vaguely
familiar come morning. A morning where I'd have to go to work. \textit{Fuck, I
  hope I'll still be vaguely drunk when I wake up. Going to work with a
  hangover would suck.}

\spacer

I got up the next morning to a headache and a dry mouth, made myself coffee,
drank a lot of water, ate something, barely remembered to take my medication on
time, and then was on my way to work, where I arrived just in the nick of time.

Once there, I made myself some more coffee (but considerably worse coffee than
I'd have made myself at home) and then went to my desk to get
started on another day of typing away slowly and trying to maintain ancient
software running on slowly failing hardware in vaguely working order. Thank
goodness I didn't have to be fully awake to accomplish that.

\spacer

A few hours later, as I was getting coffee for what must've been the fifth time
that day, I met Melissa in the kitchen, told her I'd found out some stuff, and
got her number to talk to her later.

The rest of the day was, now that I knew it didn't have to be this way,
incredibly boring. When I finally got home and called Melissa, I was close to
falling asleep and spent a lot of time just babbling at her. I think she got the
gist, but I couldn't be sure of that until the next morning, anyhow.

\chapter{Capture}



%% TODO: a bit more prologue? Just about a bit of day that kinda sucks, and
%% about being totally on board with fucking over SpaceTech. Melissa agreeing to
%% the plan to put them and a bunch of their people on the next MCT that's
%% Marsbound.

%% TODO: more. Whatever form that takes.

\end{document}

%% chapter 2 idea
%% in medias res, on the way to Mars, with Alex reminiscing a bit about how she
%% got here, and how she made sure that the ship would all have people wanting
%% to go to the same place on it. Their destination is Mars, where they'll need
%% to lay over and refuel to make the trip to the Jovian system.
%% imply that some real heist movie shit went down to get everything to this
%% point. I can't write that for shit, so it's going to have to stay implied.

%% chapter 3: arrival at Mars. Confrontation with security forces, forging of
%% required documents, required signatures etc. to keep things quiet so they can
%% refuel and make their way to the Jovian system in time.

%% set up a bit more of the Dorsa Brevia document, and write a preamble
%% including it's history?

%% so maybe I could carry this on with the main character making their way
%% to Uranus, either Miranda or Titania.

%% On Miranda, there's a city built into a large fault that's the cultural
%% and industrial center of
%% the moon, built along the walls of the fault, with a bunch of bridges linking
%% both sides. Sorta like Buda and Pest, but with way more distance, some
%% cultural differences (dunno if Buda and Pest have those), and significant
%% differences looks wise (one side was founded by people who really don't want
%% government telling them what to do, the other side was founded by people who
%% do want a government; as such, one side is fairly regular, things are
%% guaranteed, there's a police force etc., but it's only a sort of
%% parliamentary democracy, i.e. kind of a demsoc thing; whereas on the other
%% side of the fault they have their own weird forms of consensus-based
%% democracy that vary as much as the visual style of the city between the
%% various boroughs).
%% Miranda also has very low gravity, and as such has a few unique architectural
%% styles that are very filigraine and distinctly Mirandan.
%% Miranda is home to more than enough automated farming equipment and
%% installations to feed the entire Uranian system, if necessary - as it once
%% did. At time of arrival of our protagonist, Miranda no longer performs this
%% function, but just serves as a sort of cultural center of the Mirandan
%% system.
%% Miranda is home to the primary shipyards of the Uranian system, and produces
%% warships (primarily demsoc side), automated mining/refining/manufacturing
%% ships (again, primarily the demsoc side), as well as shuttles, passenger
%% and goods transportation ships (both sides), as well as trans-neptunian
%% and extrasolar colonization fleets (anarchist side).
%% It is also home to what is by far the most advanced research laboratories
%% outwards of the Jovian system, again on the anarchist side (as most
%% scientists have chosen to settle here, for various reasons).
%% There is a significant amount of Discordians on Miranda that not even
%% semi-seriously adhere to the religion, and are making preparations for moving
%% out to 136199 Eris. This is, in fact, the primary reason why so many
%% exploration and colonization ships are built on Miranda - the people are
%% already there, they know they'll need time, they're frequently bored, and
%% they're happy to help others. Also, they're *extremely* good at their jobs.
%% There's a significant contingent of geologists very much intent on studying
%% Triton, who are the primary people to have talked the Discordians into
%% building ships for them, and also the ones known to get on with the
%% Discordians best - and who share in their predilections for massive parties
%% with lots of drinking.

%% On Titania, there's a lot of manufacturing, and a few smaller, more
%% rural-feeling settlements of a few hundred people each. Manufacturing's
%% largely automated, and a lot of it services Miranda, but the inhabitants of
%% Titania don't mind that too much. They do their thing, and have a nice,
%% quiet, comfortable life filled with difficult, but fulfilling work.

%% Oberon is home to all fully automatable manufacturing, and has a
%% correspondingly low population. Certain chemical processes in use on Oberon
%% may make human habitation on the planetoid difficult, if no intervention is
%% made. This is planned, but has been pushed back repeatedly
%% in order to finish the Neptunian and trans-neptunian exploration and
%% automated colonization fleets.