It'd been a long time coming, but after over a year of travel - opposition
really wasn't the best time to make the journey - we were finally
coming up on our capture burn and subsequent aerobraking into a low Martian
orbit.

The trajectory we chose called for us to hit an altitude of 50km above
the datum of Mars at periapse. We'd done an adjustment burn for that several
weeks ago, then shut the reaction control system back down. It was now time to
do an all-engine burn as close to periapse as possible, so as to use as little
fuel as possible.

That meant an acceleration well in excess of 2G, raising up to
about 3G, so we'd spent the past few days putting everything away, as well as
taping, nailing, and screwing everything shut that could be. Since the about
hundred and fifty of us had started living on this ship quite a while ago, it
was a lot.

And now we were a few hours away from the burn that a few of us would
definitely pass out from and some might need medical attention after (we
\textit{really} hadn't planned this as well as we could have, which was not
insignificantl my fault), and we still weren't entirely done. Or at least not in
a way that I was satisfied with. Call me crazy, but I don't think leaving all
the fluids in the 0G coffee machine is a good idea when the manual for it
explicitly says not to do that when the device could experience thrust.

So it transpired that I was floating around in the kitchen of our antiquated
oft-reused Starship, near the coffee machine, with a roll of gaffa tape, trying
desperately to find all the places the machine could leak - it was thankfully
already screwed down - when Melissa came in, wrong way up as far as I was
concerned, braced herself against a wall, hooking a foot into a handhold, and
started trying to drag me out of the room, presumably towards a still-available
seat I could be strapped into. I, of course, wasn't done with the coffee
machine, and tried to indicate as much by madly flailing about.

``Is it already time?'' I asked her, after she kept trying to drag me out of the
room. She nodded, and kept dragging me to our cabin. We were one of the few
roommates to have stayed that way since the start of the journey. Most everyone
else had shuffled around, trying to find someone they were more
roommate-compatible with.

I let myself reminisce a bit as I let myself get led to my seat and strapped in.
I didn't expect we'd ever make it this far.

%% TODO
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../escape to uranus"
%%% End: